Equalizer 2.0 --\\Convergence of a Parallel Rendering Framework

### 2018-02-08 paperIEEE.tex
hardware again
git-svn-id: https://dev.ifi.uzh.ch/vmml/svn/Equalizer16@114 db7c848b-7755-4df2-b763-8796797afa52

We conducted performance benchmarks for the decomposition modes on a
rendering cluster using hexacore Intel Xeon E5-2620v3 CPUs ($2.4$\,GHz), $16$\,GB DDR4 RAM per node, and nVidia GTX $970$ GPUs with $4$\,GB VRAM each. The nodes are connected via a $40$\,Gbit/s {\em Infiniband} network.
GCC 4.8 has been used with CMake 3.7 release mode settings to compile the software stack.

>>>>

We conducted performance benchmarks for the decomposition modes on a
rendering cluster using hexacore Intel Xeon E5-2620v3 CPUs (2.4\,GHz), 16\,GB DDR4 RAM per node, nVidia GTX 970 GPUs with 4\,GB VRAM each, and QDR Infiniband.
GCC 4.8 has been used with CMake 3.7 release mode settings to compile the software stack.
